Generalized spaces for constructive algebra

### 2020-04-09 paper-herrsching2019/main.tex
Where to go from here

\subsection*{Introduction}
\addcontentsline{toc}{section}{Introduction}

@@

\paragraph{Remark on the metatheory.}
Unlike some other texts on locales or sheaves, this text is set in a
constructive (but impredicative) metatheory. We do not use the law of excluded
middle nor any version of the axiom of choice, and we also do not adopt any
nonclassical principles. We freely use powersets, but more for linguistic
convenience than by necessity.

In particular, the central idea presented in
Section~\ref{sect:appl}, the reduction technique by which we can pretend that any
given reduced ring is a field, is very robust with respect to the metatheory.
Even though we chose a semantic point of view for its derivation, the final
result is a purely syntactical transformation. As it stands, this text could be
formalized in the kind of type theory which is valid in
toposes~\cite{maietti:modular-correspondence} or in~\textsc{izf}~\cite{crosilla:cst-izf}.

@@

>>>>

\subsection*{Introduction\footnote{
Unlike some other texts on locales or sheaves, this text is set in a
constructive (but impredicative) metatheory. We do not use the law of excluded
middle nor any version of the axiom of choice, and we also do not adopt any
nonclassical principles. We freely use powersets, but more for linguistic
convenience than by necessity.
In particular, the central idea presented in
Section~\ref{sect:appl}, the reduction technique by which we can pretend that any
given reduced ring is a field, is very robust with respect to the metatheory.
Even though we chose a semantic point of view for its derivation, the final
result is a purely syntactical transformation. As it stands, this text could be
formalized in the kind of type theory which is valid in
toposes~\cite{maietti:modular-correspondence} or
in~\textsc{izf}~\cite{crosilla:cst-izf}.}}

\addcontentsline{toc}{section}{Introduction}

@@

\paragraph{Where to go from here.} The themes which this contribution touches
on are embedded into a larger context, and we invite readers to follow those
interesting tangents.

Regarding spaces, the notion of locales can be modified in several ways.
Firstly, there are \emph{sites} and closely related
\emph{toposes}.~\cite{leinster:introduction,moerdijk-maclane:sheaves-logic}.
Given two opens~$U$ and~$V$ of a locale, there is only a truth value as to
whether~$U$ is contained in~$V$; with sites and toposes, there can be a
nontrivial \emph{set} of ways that~$U$ is contained in~$V$. In an orthogonal
direction, there is the notion of a \emph{formal
topology}~\cite{sambin:some-points,sambin:ifs}. These implement the idea of
pointfree topology in predicative settings.

Regarding sheaf semantics, Section~\ref{sect:sheaf-semantics} only presents
the first-order case, but the theory can be extended include unbounded
quantification~\cite{shulman:stack-semantics}, function types and power types
and even a fully-fledged type theory~\cite{maietti:modular-correspondence}. The
sheaf semantics of appropriate toposes has been used to give \emph{synthethic
accounts} of several fields, such as differential geometry~\cite{kock:sdg},
domain theory~\cite{hyland:synthetic-domain-theory} and computability
theory~\cite{bauer:synthetic-computability-theory}.

Regarding constructive algebra, there are by now several
textbooks~\cite{mines-richman-ruitenburg:constructive-algebra,lombardi-quitte:constructive-algebra,yengui:constructive-commutative-algebra}
on constructive algebra available and there is a vast literature on
the intriguing subject of constructivizing classical commutative algebra.
Starting points include
Refs.~\refcite{coste-lombardi-roy:dynamical-method,coquand-lombardi:logical-approach,rinaldi-schuster-wessel:edde,cederquist-coquand:entrel}.

@@

XXX: Two views on A~
XXX: Direct definition of A~ possible
